Intrinsic alignments from projected tidal fields: non-linear impact on cosmic shear probes

### 2024-03-27 paper_IA.tex
Add more equations about delta-NLA model

@@

\begin{figure}
\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5. The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq. \ref{eq:bta_rescale}.  }
\label{fig:xi_deltaNLA_rescaled}
\end{figure}

>>>>

Finally, we note that fully modelling our infusion method includes contributions beyond one-loop calculations in the $II$ term. Indeed, the two-point function correlating ellipticities (Eq. \ref{eq:tidal_th_deltaNLA}) between redshift bins $i,j$ is given by:
 \begin{eqnarray}
\langle \epsilon_{i}^{\delta-\rm NLA} \epsilon_{j}^{\delta-\rm NLA}\rangle &=& \langle \epsilon_{i}^{\rm NLA}\times(1 + b_{\rm TA}\delta_i) \epsilon_{j}^{\rm NLA}\times(1 + b_{\rm TA}\delta_j)\rangle\\
&=& \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\rangle \nonumber \\
&+& b_{\rm TA} \times \left(\langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_j  \rangle + \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \rangle \right)\nonumber\\
&+& b_{\rm TA}^2 \langle \epsilon_{i}^{\rm NLA}  \epsilon_{j}^{\rm NLA}\delta_i  \delta_j \rangle \, ,
\label{eq:2pcf_deltaNLA}
\end{eqnarray}
where the last term is fourth order and involves two-loop calculations. For this reason, our $\delta$-NLA model is not expected to be well described by the one-loop calculations. Note that replacing one of the ellipticity terms by the cosmic term includes only terms up to third order in the field (e.g $\langle \epsilon_{i}^{NLA}\delta_i \gamma_j \rangle$, ...), hence  we expect the GI term to be well described. The above equation also predict that the deviations from one-loop theory scales as $b_{\rm TA}^2$, hence should be larger for population that are more biased.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{graphs/xip_deltaNLA_bta1.jpg}
\includegraphics[width=\columnwidth]{graphs/frac_xip_bta1_rescaled}
\caption{Ratio between the shear correlation functions with and without IA in tomographic bin combination 2-5. The brown and green symbols show measurements from simulations constructed with $b_{\rm TA}$ = 0.0 and 2.0 respectively,  the black solid and dotted lines shown their predictions, while the blue symbols are obtained by rescaling $b_{\rm TA}$ = 1.0 simulations using Eq. \ref{eq:bta_rescale}.  }
\label{fig:xi_deltaNLA_rescaled}
\end{figure}
